Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-10-24 cbm-rbd-paper.tex
coputaton complexity comments for Rsysnow

that the components in the system age $\tnow$.

@@

Next, we will describe how an adaptive maintenance policy based on \eqref{eq:sysrel-tnow}
can be obtained.

>>>>

that the components in the system have the age $\tnow$.

@@

For each prediction time $t$,
\eqref{eq:sysrel-tnow} is a sum over over $\prod_{k=1}^K (\cknow + 1)$ terms;
however, some of these terms correspond to $\Phinow(l_1,\ldots,l_K) = 0$,
which can thus be disregarded.
For each of the remaining terms,
we must calculate the product $\prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)$.
For all products, the constituting factors can be taken from the same table
enumerating $P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)$ for all $l_k \in \{0, 1, \cknow\}$, $k=1\ldots,K$,
so \eqref{eq:postpred-priorparams} needs to be invoked 
only $\sum_{k=1}^K (\cknow + 1)$ times.

We will evaluate \eqref{eq:sysrel-tnow} on a dense grid of prediction times $t > \tnow$,
thus discretely approximating the RLD.
As the evaluation of \eqref{eq:sysrel-tnow} for each $t$ does not involve any complex numeric calculations or Monte Carlo sampling,
the grid of prediction values can be very fine.

Next, we will describe how an adaptive maintenance policy based on %\eqref{eq:sysrel-tnow}
such a fine discrete approximation of the RLD can be obtained.
